---
title: "Ejercicios ggplot2 en R"
author: "Antonio David Villegas Yeguas"
date: "7/10/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Ejercicios de ggplot2 en R

Para cargar ggplot2

```{r}
library(ggplot2)
```

## Plot distance against stretch:

```{r}
ex1 <- data.frame(stretch=c(46,54,48,50,44,42,52), distance=c(148,182,173,166,109,141,166))

ggplot(data = ex1, aes(x = distance, y = stretch)) + 
	geom_point() +
	labs(title = "Distance vs Stretch", x = "Distance", y = "Stretch")

```


## The follwing data have ten observations taken during the years 1970-79, on October snow cover for Eurasia (snow cover is in millions of square kilometers).

```{r}
ex2 <- data.frame(year=c(1970:1979), snow.cover=c(6.5,12.0,14.9,10.0,10.7,7.9,21.9,12.5,14.5,9.2))
```

1. Plot snow.cover versus year:

```{r}
ggplot(data = ex2, aes(x = year, y = snow.cover)) + 
	geom_line() +
	labs(title = "Eurasia: Snow cover vs Year", x = "Year", y = "Snow cover (millions of square km)")

```

2. Plot a histogram of the snow.cover values:

```{r}
ggplot(data = ex2, aes(x = snow.cover)) + 
	geom_histogram(binwidth = 2) +
	labs(title = "Eurasia: Snow cover histogram", x = "Snow cover")

```






## Given the following data:

1. Create a function to convert ºF to ºC and in (inches) to mm.

2. Plot Year vs. Warmest Minimum Temperature.

3. Plot Year vs. Warmest Minimum Temperature and Coldest Minimum Temperature. Don’t forget to add a legend!



