---
title: "Ejercicios ggplot2 en R"
author: "Antonio David Villegas Yeguas"
date: "8/10/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Ejercicios de ggplot2 en R

Para cargar ggplot2

```{r}
library(ggplot2)
```

## Plot distance against stretch:

```{r}
ex1 <- data.frame(stretch=c(46,54,48,50,44,42,52), distance=c(148,182,173,166,109,141,166))

ggplot(data = ex1, aes(x = distance, y = stretch)) + 
	geom_point() +
	labs(title = "Distance vs Stretch", x = "Distance", y = "Stretch")

```


## The follwing data have ten observations taken during the years 1970-79, on October snow cover for Eurasia (snow cover is in millions of square kilometers).

```{r}
ex2 <- data.frame(year=c(1970:1979), snow.cover=c(6.5,12.0,14.9,10.0,10.7,7.9,21.9,12.5,14.5,9.2))
```

1. Plot snow.cover versus year:

```{r}
ggplot(data = ex2, aes(x = year, y = snow.cover)) + 
	geom_line() +
	labs(title = "Eurasia: Snow cover vs Year", x = "Year", y = "Snow cover (millions of square km)")

```

2. Plot a histogram of the snow.cover values:

```{r}
ggplot(data = ex2, aes(x = snow.cover)) + 
	geom_histogram(binwidth = 2) +
	labs(title = "Eurasia: Snow cover histogram", x = "Snow cover")

```






## Given the following data:

```{r}
library(readr)
datos <- read_csv("datos.csv", col_types = "d")
# algunos los lee como char, de ahi el cambio
datos <- as.data.frame(lapply(datos, as.double))
datos
# para trabajar mejor con los datos
# todo en minuscula, cambio espacios por _ y sin parentesis
nuevos_nombres <- tolower(colnames(datos))
nuevos_nombres <- lapply(nuevos_nombres, gsub, pattern = "..", replacement = "_", fixed = TRUE)
nuevos_nombres <- unlist(lapply(nuevos_nombres, gsub, pattern = ".", replacement = "_", fixed = TRUE))
nuevos_nombres
colnames(datos) <- nuevos_nombres
summary(datos)
```


1. Create a function to convert ºF to ºC and in (inches) to mm.

```{r}
fahrenheit_to_celsius <- function(val) {
	val - 32 / 1.8
}

inches_to_milimeters <- function(val) {
	val * 25.4
}

# las columnas de grados le aplicamos la función para cambiar a celsius
datos[2:8] <- lapply(datos[2:8], fahrenheit_to_celsius)

# le cambiamos el nombre, las que acaban por _f por _c
nuevos_nombres <- unlist(lapply(colnames(datos), gsub, pattern = "_f_", replacement = "_c", fixed = TRUE))
colnames(datos) <- nuevos_nombres
datos

# las columnas de pulgadas le aplicamos la función para cambiar a mm
datos[9:12] <- lapply(datos[9:12], inches_to_milimeters)

# le cambiamos el nombre, para que las que son in, pasen a mm
nuevos_nombres <- unlist(lapply(colnames(datos), gsub, pattern = "_in_", replacement = "_mm", fixed = TRUE))
colnames(datos) <- nuevos_nombres
datos


```


2. Plot Year vs. Warmest Minimum Temperature.

```{r}

ggplot(data = datos, aes(x = year, y = warmest_minimum_temperature_c)) + 
	geom_line() +
	labs(title = "Year vs Warmest Minimum Temperature", x = "Year", y = "Warmest Minimum Temperature (Celsius)")

```

3. Plot Year vs. Warmest Minimum Temperature and Coldest Minimum Temperature. Don’t forget to add a legend!


```{r}
ggplot(data = datos, aes(x = year)) + 
	geom_line(aes(y = warmest_minimum_temperature_c, color = "Warmest Minimum")) +
	geom_line(aes(y = coldest_minimum_temperature_c, color = "Coldest Minimum")) +
	labs(title = "Year vs Warmest Minimum Temperature and Coldest Minimum Temperature", x = "Year", y = "Temperature (Celsius)") +
	scale_color_manual(name = "Temperatures", values = c("Warmest Minimum" = "red", "Coldest Minimum" = "blue"))

```



